paper

### 2019-01-05 Report/paper.tex

    As a starting point we have papers of 4 years spanning 2015 to 2018 of
the proceedings of ICLS, which is held in even years, respectively CSCL,
held in odd years. The overall number of papers per year can be observed
in figure \(\ref{fig1}\). The provided raw dataset consists of papers in
pdf format as well as associated metadata in xml format. To extract
information from the dataset we first need to convert the data a format
that is more adapt to the task of data exploration and handling with a
variety of external libraries. We store the data we extract from the
provided dataset in csv format, as this makes it accessible to any
scientist and is unlikely to become an obsolete any time soon.

@@

@@

@@

    \begin{figure}
        \begin{center}\adjustimage{max size={\linewidth}{0.4\paperheight}}{paper_files/paper_35_0.png}\end{center}
        \caption{Variation of steady-state oscillation amplitude with driving frequency for an oscillator with undamped frequency of 100 Hz, a driving amplitude $A = 10^6$, and various damping constants.}
        \label{figtest}
    \end{figure}

>>>>

    As a starting point we have papers of 4 years spanning 2015 to 2018 of
the proceedings of ICLS, which is held in even years, respectively CSCL,
held in odd years. The overall number of papers per year is shown in
figure \(\ref{fig1}\). The provided raw dataset consists of papers in
pdf format as well as associated metadata in xml format. To extract
information from the dataset we first need to convert the data a format
that is more adapt to the task of data exploration and handling with a
variety of external libraries. We store the data we extract from the
provided dataset in csv format, as this makes it accessible to any
scientist and is unlikely to become an obsolete any time soon.

@@

    \hypertarget{co-authorship-graphs}{%
\subsection{Co-authorship graphs}\label{co-authorship-graphs}}

\hypertarget{interactive-map-visualizations}{%
\subsection{Interactive Map
visualizations}\label{interactive-map-visualizations}}

@@

    \hypertarget{community-composition-structure}{%
\subsection{Community Composition \&
Structure}\label{community-composition-structure}}

We find that participants from 372 institutions participated over the
last 4 years, with a median of 128 institutions per year. Numbers of
institutions participating are increasing each year, with a noticeable
peak in 2018, which participants from 261 institutions. This is a
considerable up from the last conference ICLS in 2016 which had 135
participating institutions. Most participants are from the US, with a
average of 50\% of all participants being from the US. We can also
observe a trend of increase in US participants with only 35\% of US
participants in 2015 and 51\% in 2017, followed by 64\% in 2018.
Overall, participants from 41 nations have participated over the 4
years, which an average of 28 nations represented each conference. After
the US, participants of Germany, Canada and Singapore make up the
biggest proportion of participants \(\ref{figrep}\).

\begin{verbatim}
1. Collaboration
2. Movement of participants
3. Citation
\end{verbatim}

    \begin{figure}
        \begin{center}\adjustimage{max size={\linewidth}{0.4\paperheight}}{paper_files/paper_33_0.png}\end{center}
        \caption{}
        \label{}
    \end{figure}

    \hypertarget{collaboration}{%
\subsubsection{Collaboration}\label{collaboration}}

\texttt{\color{outcolor}Out[{\color{outcolor}135}]:}

    \begin{figure}
        \begin{center}\adjustimage{max size={\linewidth}{0.4\paperheight}}{paper_files/paper_35_0.png}\end{center}
        \caption{Collaborative papers between countries}
        \label{figcollab}
    \end{figure}

    \hypertarget{research-topics-in-the-community}{%
\subsection{Research topics in the
Community}\label{research-topics-in-the-community}}

\begin{verbatim}
1. Keywords
2. Outside influence: Conferences being sited
\end{verbatim}

@@

    \begin{figure}
        \begin{center}\adjustimage{max size={\linewidth}{0.4\paperheight}}{paper_files/paper_42_0.png}\end{center}
        \caption{Variation of steady-state oscillation amplitude with driving frequency for an oscillator with undamped frequency of 100 Hz, a driving amplitude $A = 10^6$, and various damping constants.}
        \label{figtest}
    \end{figure}
